### 2023-06-01 paper/localpsf.tex
move adv pcg and geigs plots to separate files

\begin{figure}
	\caption{Impulse responses for various diffusivities kappa and fixed simulation time Tf=0.5 (top) and simulation times with fixed kappa=1e-3 (bot).}
	\label{fig:adv_vary_kappa_tf}
\end{figure}

\begin{figure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\begin{tikzpicture}[baseline, trim axis right]
		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
		ymode=log,
		ymin=1e-11,
		ymax=2,
		xmax=1000,
		axis x line*=bottom,
		axis y line*=left,
		xtick={0, 200, 400, 600,800,1000},
		xlabel={CG iteration},
		ylabel={$\|\bm{x}_k - \bm{x}\|/\|\bm{x}\|$},
		title={CG convergence},
		legend style={at={(1.2,1)},anchor=north east},
		%legend pos=north east,
		legend style={font=\small}
		]
		\addlegendentry{Reg}
		\addplot[dotted, line width=0.5mm] table {advDiff_cg_rand_errs_reg.dat};
		\addlegendentry{None}
		\addplot[dash dot, line width=0.5mm] table {advDiff_cg_rand_errs_none.dat};
		\addlegendentry{PSF (1)}
		\addplot[blue, line width=0.5mm] table {advDiff_cg_rand_errs_psf1.dat};
		\addlegendentry{PSF (5)}
		\addplot[red, line width=0.5mm] table {advDiff_cg_rand_errs_psf5.dat};
		\addlegendentry{PSF (25)}
		\addplot[purple, line width=0.5mm] table {advDiff_cg_rand_errs_psf25.dat};
		\end{axis}
		\end{tikzpicture}
		\caption{}
		\label{fig:adv_cg_convergence}
	\end{subfigure}
	\begin{subfigure}{0.49\textwidth}
		\centering
		\begin{tikzpicture}[baseline, trim axis right]
\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
ymode=log,
xmin=-50,
xmax=600,
ymax=1.e6,
title={Generalized eigenvalues},
xlabel={$k$, generalized eigenvalue \#},
ylabel={$\lambda_{k}$},
xtick={0, 300, 600, 900, 1200},
%legend pos=north east,
legend style={font=\small},
ylabel near ticks, ylabel shift={-6pt},
axis x line*=bottom,
axis y line*=right,
%legend style={at={(0.95,1)},anchor=north east},
]
%\addlegendentry{REG}
\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {advDiff_generalizedEigenvalues.dat};
\addplot[dash dot, line width=0.5mm] table[x=k, y=none] {advDiff_generalizedEigenvalues.dat};
%\addlegendentry{PSF (1)}
\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {advDiff_generalizedEigenvalues.dat};
%\addlegendentry{PSF (5)}
\addplot[red, line width=0.5mm] table[x=k, y=psf5] {advDiff_generalizedEigenvalues.dat};
%\addlegendentry{PSF (25)}
\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {advDiff_generalizedEigenvalues.dat};
\end{axis}
\end{tikzpicture}
		\caption{}
		\label{fig:adv_generalized_eigenvalues}
	\end{subfigure}
	\caption{Left (\ref{fig:adv_cg_convergence}) shows the convergence history for solving $\bm{H} \bm{x} = \bm{b}$ using PCG, where $\bm{b}$ has i.i.d. random entries drawn from the standard normal distribution. BLAH BLAH BLAH
		%		The y-axis is $\|b-Hx_k\|/\|b\|$, where $x_k$ is the $k$th PCG iterate. 
		Here we use $\gamma=7.88 \times 10^{-6}$, which is determined by the Morozov discrepancy principle. Results in these figures are shown for our preconditioner with 5, 15, and 30 batches (PSF (5), PSF (15), and PSF(30), respectively), regularization preconditioning (REG), and no preconditioning (NONE). The preconditioner is constructed using $\bm{H}_\text{gn}$.}
	\label{fig:adv_krylov_convergence}
\end{figure}

>>>>

\begin{figure}
	\caption{Impulse responses for various diffusivities kappa and fixed simulation time Tf=0.5 (top) and simulation times with fixed $\kappa=1e{-3}$ (bot).}
	\label{fig:adv_vary_kappa_tf}
\end{figure}

\begin{figure}
	\begin{subfigure}{0.52\textwidth}
		\centering
		\includegraphics[scale=1.0]{adv_pcg_convergence.pdf}
%		\begin{tikzpicture}[baseline, trim axis right]
%		\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
%		ymode=log,
%		ymin=1e-11,
%		ymax=2,
%		xmax=1000,
%		axis x line*=bottom,
%		axis y line*=left,
%		xtick={0, 200, 400, 600,800,1000},
%		xlabel={CG iteration},
%		ylabel={$\|\bm{x}_k - \bm{x}\|/\|\bm{x}\|$},
%		title={CG convergence},
%		legend style={at={(1.2,1)},anchor=north east},
%		%legend pos=north east,
%		legend style={font=\small}
%		]
%		\addlegendentry{Reg}
%		\addplot[dotted, line width=0.5mm] table {advDiff_cg_rand_errs_reg.dat};
%		\addlegendentry{None}
%		\addplot[dash dot, line width=0.5mm] table {advDiff_cg_rand_errs_none.dat};
%		\addlegendentry{PSF (1)}
%		\addplot[blue, line width=0.5mm] table {advDiff_cg_rand_errs_psf1.dat};
%		\addlegendentry{PSF (5)}
%		\addplot[red, line width=0.5mm] table {advDiff_cg_rand_errs_psf5.dat};
%		\addlegendentry{PSF (25)}
%		\addplot[purple, line width=0.5mm] table {advDiff_cg_rand_errs_psf25.dat};
%		\end{axis}
%		\end{tikzpicture}
		\caption{}
		\label{fig:adv_cg_convergence}
	\end{subfigure}
	\begin{subfigure}{0.47\textwidth}
		\centering
		\includegraphics[scale=1.0]{adv_geigs_figure.pdf}
%		\begin{tikzpicture}[baseline, trim axis right]
%\begin{axis}[width=0.99\linewidth, height=1.0\linewidth,
%ymode=log,
%xmin=-50,
%xmax=600,
%ymax=1.e6,
%title={Generalized eigenvalues},
%xlabel={$k$, generalized eigenvalue \#},
%ylabel={$\lambda_{k}$},
%xtick={0, 300, 600, 900, 1200},
%%legend pos=north east,
%legend style={font=\small},
%ylabel near ticks, ylabel shift={-6pt},
%axis x line*=bottom,
%axis y line*=right,
%%legend style={at={(0.95,1)},anchor=north east},
%]
%%\addlegendentry{REG}
%\addplot[dotted, line width=0.5mm] table[x=k, y=reg] {advDiff_generalizedEigenvalues.dat};
%\addplot[dash dot, line width=0.5mm] table[x=k, y=none] {advDiff_generalizedEigenvalues.dat};
%%\addlegendentry{PSF (1)}
%\addplot[blue, line width=0.5mm] table[x=k, y=psf1] {advDiff_generalizedEigenvalues.dat};
%%\addlegendentry{PSF (5)}
%\addplot[red, line width=0.5mm] table[x=k, y=psf5] {advDiff_generalizedEigenvalues.dat};
%%\addlegendentry{PSF (25)}
%\addplot[purple, line width=0.5mm] table[x=k, y=psf25] {advDiff_generalizedEigenvalues.dat};
%\end{axis}
%\end{tikzpicture}
		\caption{}
		\label{fig:adv_generalized_eigenvalues}
	\end{subfigure}
	\caption{Left (\ref{fig:adv_cg_convergence}) shows the convergence history for solving $\bm{H} \bm{x} = \bm{b}$ using PCG, where $\bm{b}$ has i.i.d. random entries drawn from the standard normal distribution. BLAH BLAH BLAH
		%		The y-axis is $\|b-Hx_k\|/\|b\|$, where $x_k$ is the $k$th PCG iterate. 
		Here we use $\gamma=7.88 \times 10^{-6}$, which is determined by the Morozov discrepancy principle. Results in these figures are shown for our preconditioner with 5, 15, and 30 batches (PSF (5), PSF (15), and PSF(30), respectively), regularization preconditioning (REG), and no preconditioning (NONE). The preconditioner is constructed using $\bm{H}_\text{gn}$.}
	\label{fig:adv_krylov_convergence}
\end{figure}
